When are Fuzzy Extractors Possible?

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
going over proofs, still need fuzzy ext imposs

\newcommand{\secref}[1]{\mbox{Section~\ref{#1}}}
\newcommand{\subsecref}[1]{\mbox{Subsection~\ref{#1}}}
\newcommand{\apref}[1]{\mbox{Appendix~\ref{#1}}}
\newcommand{\thref}[1]{\mbox{Theorem~\ref{#1}}}
\newcommand{\exref}[1]{\mbox{Example~\ref{#1}}}
\newcommand{\defref}[1]{\mbox{Definition~\ref{#1}}}
\newcommand{\corref}[1]{\mbox{Corollary~\ref{#1}}}
\newcommand{\lemref}[1]{\mbox{Lemma~\ref{#1}}}
\newcommand{\assref}[1]{\mbox{Assumption~\ref{#1}}}
\newcommand{\probref}[1]{\mbox{Problem~\ref{#1}}}
\newcommand{\clref}[1]{\mbox{Claim~\ref{#1}}}
\newcommand{\propref}[1]{\mbox{Proposition~\ref{#1}}}
\newcommand{\remref}[1]{\mbox{Remark~\ref{#1}}}
\newcommand{\consref}[1]{\mbox{Construction~\ref{#1}}}
\newcommand{\figref}[1]{\mbox{Figure~\ref{#1}}}
\DeclareMathOperator*{\expe}{\mathbb{E}}
\DeclareMathOperator*{\var}{\text{Var}}

@@

Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  We denote the ball with the largest number of points as $B_{t, max}$.  Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)\nonumber \\
&= \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}

@@

@@

\section{Proof of \propref{prop:fuzz necessary}}
\label{sec:proof fuzz necessary}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(w', p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
Note that $D$ only provides an input and looks at the output, thus it works in the interactive setting.  Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.  Thus, $D$ is also a distinguisher in the computational setting.
\end{proof}

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ recall that the size of $W^*$ is at most $B_{t, max}$ and since $w, w'$ are chosen independently of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash, our goal is to bound the probability that another element $w^*$ collides, that is $F(K, w^*) = F(K, w)$.
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, max}|-1$.  This completes the proof.
\end{proof}

\section{Proof of \thref{thm:layered hashing}}
\label{sec:proof of layered hashing}
\begin{proof}
We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]

\noindent
\textbf{Correctness:}  We begin by arguing correctness.  We set $n = \ell$ to be the number of levels.\footnote{This proof can be carried out for an arbitrary $\ell$ but it leads to a more complicated theorem statement.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(m+\ell)} = 2^{-(m+n)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(m+n)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

\textbf{Ideal Adversary with access to Level Information:} Before arguing security of the actual construction, we consider the optimum performance of an adversary that receives the level information.  %We first consider the optimum strategy for an adversary that receives just the information about the probability of $w$.  
An adversary that receives $i$ as input the best strategy is to guess a point that has the most nearby weight in that level.  That is, $w^*\leftarrow A(i)$ such that $\max_{w^* \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i}}[\dis(w, w^*)]$. The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  Note there are $n$ outcomes for $i$ so the overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}\le \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \label{eq:link fuzz 1}\\
&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\label{eq:link fuzz 2}\\
&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  That is, $\sum_{w | \Pr[W=w]\le 2^{-(n+m)}}\Pr[W = w] \le 2^{-m}$.  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-n}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | \Pr[W=w]>2^{-(n+m)}}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equations~\eqref{eq:link fuzz 1}-\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

\section{Proof of \thref{thm:imposs sketch}}
\label{sec:proof secure sketch imposs}
The proof of \thref{thm:imposs sketch} uses the definition of a Shannon code: 
\begin{definition}
\label{def:shannon-code}
Let $C$ be a set over space $\mathcal{M}$.  We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in C$, $\Pr[c'\leftarrow B_t(c) \wedge \rec(c') \neq c]\le \delta$. %To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
\end{definition}

We now prove item in the outline of \thref{thm:imposs sketch}.

\begin{proposition} 
\label{prop:each element good} For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some $W\in\mathcal{W}$.  The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.  Recall that $t< \gamma$.  We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma$ and thus $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.  Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.  That is, $\dis (w, w')  =\gamma$.
\end{proof}

@@

\begin{lemma}
\label{lem:secure sketch entropy loss}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  We do not consider these coins in our security analysis~(and thus, they can be considered private).
By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) = w] >1-\delta.
\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
Fix some $w$.  
By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[ss\in A_{ss}]\ge 1/2$ and $\forall ss\in A_{ss}$, 
\[
\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

Consider some $ss^*\in A_{ss}$.  We now show that $H_0(V | \sketch(V) = ss^*) \le (\gamma-t+1)\log |\mathbb{F}|$.  Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.  Thus for every value in $V|\sketch(V) = ss^*$ this is also true.  This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  In particular, this implies that for all $w_1, w_2 \in V|\sketch(V)=ss^*$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|\sketch(V)=ss^*$ is a set with minimum distance at least $t$.  By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
\end{proof}

\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <1$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.  We show having seen $V$ there are many possible values for $Z$~(and the distributions $V|Z$ have disjoint support outside of the observed point).  The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

We now show for any sketch algorithm, for possible values of $Z$ conditioned on $V=v$ there are few points included in the support of $V |\sketch(V)$.  The distributions $V | Z=z_1$ and $V| Z=z_2$ for possible $z_1, z_2$~(having seen $v$) overlap only at the point $v$.  This means for any $v^*\in V| \sketch(V)$ (other than the true $v$) there is at most one $z$ such that $v^*\in V | \sketch(V), Z=z$.  Thus, the optimum strategy is to include these values uniformly from different $Z$ values.

>>>>

\newcommand{\secref}[1]{\mbox{Section~\ref{#1}}}
\newcommand{\subsecref}[1]{\mbox{Subsection~\ref{#1}}}
\newcommand{\apref}[1]{\mbox{Appendix~\ref{#1}}}
\newcommand{\thref}[1]{\mbox{Theorem~\ref{#1}}}
\newcommand{\exref}[1]{\mbox{Example~\ref{#1}}}
\newcommand{\defref}[1]{\mbox{Definition~\ref{#1}}}
\newcommand{\corref}[1]{\mbox{Corollary~\ref{#1}}}
\newcommand{\lemref}[1]{\mbox{Lemma~\ref{#1}}}
\newcommand{\assref}[1]{\mbox{Assumption~\ref{#1}}}
\newcommand{\probref}[1]{\mbox{Problem~\ref{#1}}}
\newcommand{\clref}[1]{\mbox{Claim~\ref{#1}}}
\newcommand{\propref}[1]{\mbox{Proposition~\ref{#1}}}
\newcommand{\remref}[1]{\mbox{Remark~\ref{#1}}}
\newcommand{\consref}[1]{\mbox{Construction~\ref{#1}}}
\newcommand{\figref}[1]{\mbox{Figure~\ref{#1}}}
\DeclareMathOperator*{\expe}{\mathbb{E}}
\DeclareMathOperator*{\var}{\text{Var}}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  We denote the ball with the largest number of points as $B_{t, max}$.  Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w')\le t\} \right|* \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w')\le t\}| *2^{-\Hoo(W)}\right) \nonumber \\
&=\Hoo(W) -\log\left( \max_{w' \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w')\le t\} |\right)\nonumber \\
&= \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}

@@

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w' \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}.
\]

@@

\section{Proof of \propref{prop:fuzz necessary}}
\label{sec:proof fuzz necessary}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $w' \in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, w')\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(w', p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
Clearly, $\Pr[D(\Key, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
Note that $D$ only provides an input and looks at the output, thus it extends to an interactive protocol.  Also, $D$ is of size $\max |\mathcal{M}|+ |\rep|$ where $\max |\mathcal{M}|$ is the longest description of an item in the metric space.  Thus, $D$ is also a distinguisher in the computational setting.
\end{proof}

@@

We now argue correctness.  Fix some $w, w'$.  Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t, max}$.  Since $w, w'$ are independent of $\sketch$ this set is independent of the choice of $\mathcal{K}$.  The algorithm  $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ collides is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R|} \le \frac{|B_{t, max}|-1}{|R|}
\end{align*}
The inequality proceeds by union bound. The first equality proceeds by the universality of $F$ and the second inequality proceeds by noting the number of wrong neighbors is bounded by $|B_{t, max}|-1$.  This completes the proof.
\end{proof}

\section{Proof of \thref{thm:layered hashing}}
\label{sec:proof of layered hashing}
\begin{proof}
Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.

\noindent
\textbf{Correctness:}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(m+\ell)} = 2^{-(m+n)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  When $\Pr[W=w]> 2^{-(m+n)}$ let $L_i^*$ be the level of $\Pr[W=w]$.

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $|B_{t, i, max}|$.

\noindent
\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.

The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses \[w^*= \argmax_{w' \in \mathcal{M}}\Pr_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w^*)}[W=w].\] The success of this adversary is at least $2^{-(i+1)}|B_{t,i, max}|$ as there at $B_{t, i, max}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-(i+1)}|B_{t, i, max}|&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) = -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
-\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:
\begin{align*}
\max_{w\in W | \Pr[W=w]>2^{-(m+n)}}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{|\sketch(W)|i|}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]*2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(2^{-i}*|B_{t, i, max}|/\delta\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}*|B_{t, i, max}|\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*|B_{t, i, max}|\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

\section{Proof of \thref{thm:imposs sketch}}
\label{sec:proof secure sketch imposs}
Let $c'\leftarrow \neigh_t(c)$ sample a uniform point within distance $t$ of $c$.  
The proof of \thref{thm:imposs sketch} uses the definition of a Shannon code: 
\begin{definition}
\label{def:shannon-code}
Let $C$ be a set over space $\mathcal{M}$.  We say that $C$ is an $(t,\delta)$-\emph{Shannon code} if there exists a procedure $\rec$ such that for all $t'\le t$ and for all $c\in C$, $\Pr[c'\leftarrow \neigh_t(c) \wedge \rec(c') \neq c]\le \delta$. %To distinguish it from the average-error Shannon code defined below, we will sometimes call it a \emph{maximal-error} Shannon code.
\end{definition}

\noindent
We now prove item in the outline of \thref{thm:imposs sketch}.

\begin{proposition} 
\label{prop:each element good} For each $W\in\mathcal{W}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some $W\in\mathcal{W}$.  The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.  We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma>t$.  This shows that $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.  Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.  That is, $\dis (w, w')  =\gamma$.
\end{proof}

@@

\begin{lemma}
\label{lem:secure sketch entropy loss}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  We do not consider these coins in our security analysis~(and thus, they can be considered private).  \bnote{is this really okay?  I know its just another markov but it makes me nervous}
By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
Fix some $w$.  
By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[ss\in A_{ss}]\ge 1/2$ and $\forall ss\in A_{ss}$, 
\[
\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

Consider some $ss^*\in A_{ss}$.  We now show that $H_0(V | \sketch(V) = ss^*) \le (\gamma-t+1)\log |\mathbb{F}|$.  For the sketched value $w$, $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.

For every value in $V|\sketch(V) = ss^*$ this is also true.  This makes the support of $V|\sketch(V)=ss^*$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  This implies that for all $w_1, w_2 \in V|\sketch(V)=ss^*$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|\sketch(V)=ss^*$ is a set with minimum distance at least $t$.

By the Singleton bound, this implies that $H_0(V |\sketch(V)=ss^*) \le (\gamma -t+1 )|\mathbb{F}|$.  Averaging over $\sketch(V)=ss^*$ one has that $\tilde{H}_0(V|P) \le (\gamma -t +1) \log|\mathbb{F}| +1$.
\end{proof}

\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <1$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.  %Having seen $V$ there are many possible values for $Z$.  Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.  
 The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

We now show for any sketch algorithm there are few possible values of $V|Z$ in the support of $V |\sketch(V)$.  The distributions $V | Z=z_1$ and $V| Z=z_2$ for possible $z_1, z_2$~(having seen $v$) overlap only at the point $v$.  This means for any $v^*\in V| \sketch(V)$ (other than the true $v$) there is at most one $z$ such that $v^*\in V | \sketch(V), Z=z$.
